---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coRPysprofiling

<!-- badges: start -->

<!-- badges: end -->

## Summary

coRPysprofiling is an open-source library designed to bring exploratory data analysis and visualization to the domain of natural language processing. Functions in the package will be used to provide some elementary statistics and visualizations for a single text corpus or provide functions to compare multiple corpora with each other.

## Installation

You can install the released version of coRPysprofiling from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("coRPysprofiling")
```

## Features

Some specific functions include:

-   corpus\_analysis: corpus analysis will generate a statistical report about the characteristics of a single corpus (e.g. unique word count, average word/sentence length, top words used, topic analysis).
-   corpus\_viz: corpus\_viz will generate relevant visualizations of a single corpus (e.g. word cloud, histograms for average word/sentence length, top words used).
-   corpora\_compare: Given two or more corpora, corpora\_compare will find similarity (e.g, Euclidean distance or cosine similarity) between each pair of corpora.
-   corpora\_best\_match: Given a reference document and two or more corpora, corpora\_best\_match will rank the corpora in the order of most relevance to the reference document.

## Relevance to the R Ecosystem

-   TODO

## Dependencies

-   TODO

## Usage

-   TODO

## Documentation

The help file can be viewed by:

```{r}
?corpus_analysis
?corpus_viz
?corpora_compare
?corpora_best_match
```

## Contributors

We welcome and recognize all contributions. You can see a list of current contributors in the contributors tab.

#### Development Team

Anita Li, Elanor Boyle-Stanley, Junghoo Kim, and Ivy Zhang

#### Credits

-   TODO
