---
title: "Introduction to coRPysprofiling"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{coRPysprofiling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The coRPysprofiling package can help you do some preliminary EDA and EDV on text data.  As well as comparing corpora to determine similarity.

```{r setup}
library(coRPysprofiling)
```

### Data

Lets start with some input text.  We are going to look at a data science job description to begin with.

```{r, attr.output='style="max-height: 100px;"'}
data_science_job <- "Apply statistical and machine learning knowledge to specific business problems and data. Develop initiatives to assist Engineering, Logistics, and Mechanical teams in a number of highly technical areas. Use data science techniques to find data patterns, anomalies, and optimization opportunities. Interpret, translate, and communicate analytical findings to business stakeholders. Tackle and solve complex analytical problems using quantitative approaches. Collaborate to implement data best practices through the Data Lab, Data Hub, and Data Lake teams. Work in an agile environment including regular meetings, sprints, Kanban, etc."
```

### Basic summary of text with `corpus_analysis`

We can use the `corpus_analysis` function to calculate some high level statistics on this text.  This will return a data frame (or tibble) with the total number of words, total number of tokens, number of unique tokens, average token length, the number of sentences and the average number of tokens in all sentences.

```{r}
corpus_analysis(data_science_job)
```

### Visualization with `corpus_viz`

We can also the corpus_viz function to generate three visualization of this corpus.  To access the individual visualizations, index the visualization object by plot name.

```{r, fig.height = 4, fig.width=6}
visuals <- corpus_viz(data_science_job)
visuals["word cloud"]
```

```{r, fig.height = 4, fig.width=6}
visuals["word freq bar chart"]
```

```{r, fig.height = 4, fig.width=6}
visuals["word length bar chart"]
```

### text comparation with `corpora_compare`

Now lets use the `corpora_compare` function to determine the similarity of two corpora, using the default metric `cosine_similarity`.  We will load another data science job description.

```{r}
data_science_job2 <- "You have spent countless hours over the years solving hard problems in mathematics, statistics and computer science. You thrive on extracting useful information from large messy data sets. You know that a data set that satisfies all the requirements of a specific statistical procedure is a rarity indeed – and you know what to do about it. You have followed your passion for all things quantitative and are turning it into your profession. At ThinkingCapital we encourage everyone to trust themselves, stop holding back and use your acquired knowledge to influence your future. Everyone in the team is an integral contributor to our products, working with our customers to collaborate and design the best solutions. Our open work culture provides the opportunity for you to contribute to all aspects of our business: customer engagement, product ownership, software, QA, devops and 24/7 cloud service deployment. As a key member of our team your passion for data will help us design, develop and deploy our integrated cloud services that help small businesses succeed." 

corpora_compare(data_science_job, data_science_job2)
```

The closer the value is to zero, the more similar the corpora are.  Sometimes you can send up with a very small numbers instead of exactly 0, this is due to rounding.  Lets check the score for two identical corpora. 

```{r}
corpora_compare(data_science_job, data_science_job)
```

We can chose to use the `euclidean` metric to calculate the similarity. Like the `cosine_similarity` metric values closer to zero are more similar and identical corpora should return a score of zero.

```{r}
corpora_compare(data_science_job, data_science_job2, metric="euclidean")
```

```{r}
corpora_compare(data_science_job, data_science_job, metric="euclidean")
```

### Compare between corpora with `corpora_best_match`

We can use the `corpora_best_match` function to rank corpora against a reference document by similarity.  Lets expand our example to include some more job descriptions, the combine those into a list. 

```{r}
accounting_job <- "Prepare balance sheets, profit and loss statements and other financial reports. Responsibilities also include analyzing trends, costs, revenues, financial commitments and obligations incurred to predict future revenues and expenses. Reports organization's finances to management and offers suggestions about resource utilization, tax strategies and assumptions underlying budget forecasts.May require a bachelor's degree in area of specialty and 2-4 years of experience in the field or in a related area. Familiar with standard concepts, practices and procedures within a particular field. Rely on experience and judgment to plan and accomplish goals. Perform a variety of tasks. Work under general supervision. A certain degree of creativity and latitude is required. Typically reports to a supervisor or manager."

admin_job <- "Administrative assistant duties and responsibilities include providing administrative support to ensure efficient operation of the office. Supports managers and employees through a variety of tasks related to organization and communication. Responsible for confidential and time sensitive material. Familiar with a variety of the field's concepts, practices and procedures. Ability to effectively communicate via phone and email ensuring that all Administrative Assistant duties are completed accurately and delivered with high quality and in a timely manner. May direct and lead the work of others. Rely on experience and judgment to plan and accomplish goals and a wide degree of creativity and latitude is expected. Typically reports to a manager or head of a unit/department."

bank_job <- "Support Investment Advisors in providing superior customer service and be available to meet client requests. Ensure effective communication between all parties (clients, advisors, internal and external agents). The candidate needs to be able to identify all risks inherent to the Wealth Management sector's activities"

sales_job <- "Direct and oversee an organization's sales policies, objectives and initiatives. Set short- and long-term sales strategies and evaluate effectiveness of current sales programs. Recommend product or service enhancements to improve customer satisfaction and sales potential. Familiar with a variety of the field's concepts, practices and procedures. Rely on extensive experience and judgment to plan and accomplish goals. Lead and direct the work of others. A wide degree of creativity and latitude is expected. Typically reports to top management. The successful candidate will understand what motivates customers to buy and know how to tap into those needs and desires in an effective way."

job_list <- c(accounting_job, admin_job, bank_job, data_science_job,
              data_science_job2, sales_job)
```

We can compare this list against our reference document. Let's use the program description from the UBC Masters of Data Science program. 

```{r}
mds <- "Are you a creative problem solver with a love for data? UBC’s Master of Data Science was designed for you. Developed to give students a fast track to a great career, the program is helping to meet a growing need by producing skilled professionals who can turn data into knowledge. Utilizing descriptive and prescriptive techniques, students extract and analyze data from both unstructured and structured forms, uncover insights, and learn to effectively communicate their results with stakeholders. Graduates are highly trained, qualified data scientists who can help businesses and organizations, across all domains, improve strategy, products, services, health, safety, and so much more by translating their findings into solutions that enable and inform action."

corpora_best_match(mds, job_list)
```

As expected the data science job descriptions are considered most similar to the UBC MDS program description. 

We can also use the `euclidean` metric to calculate the similarity.

```{r}
corpora_best_match(mds, job_list, metric = "euclidean")
```


